### 2020-12-22 README.Rmd
center epbmclogo
update centering
Update readme.rmd

  ![epbmclogo](analysis/data/derived_data/horse_DNA_image.png#style=centerme)

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown document which includes code to reproduce the figures generated by in our analysis.
  - [:file\_folder: data](/analysis/data): Supplementary data files and metadata used in this analysis

@@

The following session information (compute environment and R/package versions) will reproduce the analysis and figures generated in the manuscript.

>>>>

|                                                                             ![epbmclogo](analysis/data/derived_data/horse_DNA_image.png#style=centerme)

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown document which includes code to reproduce the figures generated by our analysis.
  - [:file\_folder: data](/analysis/data): Supplementary data files and metadata used in this analysis

@@

Session information (computer environment and R/package versions) were used to generate the analyses and figures in the manuscript:
